---
title: "Cesana et al: Means and ANOVA results, Exp 1-4"
author: ""
date: "17 4 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(CODreports) # custom report functions
library(afex)
```

```{r data processing}
data1 <- read_tsv("../data/InfantsData/ByTrial_LookingTime/E1-byTrial.txt")
str(data1)

data2 <- read_tsv("../data/InfantsData/ByTrial_LookingTime/E2-byTrial.txt")
str(data2)

data3 <- read_tsv("../data/InfantsData/ByTrial_LookingTime/E3-byTrial.txt")
str(data1)

data4 <- read_tsv("../data/InfantsData/ByTrial_LookingTime/E4-byTrial.txt")
str(data2)

data5 <- read_tsv("../data/InfantsData/ByTrial_LookingTime/E5-byTrial.txt")
str(data2)

data6 <- read_tsv("../data/InfantsData/ByTrial_LookingTime/E6-byTrial.txt")
str(data2)
```
### Summarize for data analysis
```{r}
exp1 <- data1 %>%
  group_by(Outcome,Participant) %>%
  summarise(mean = mean(LookingTime))%>%
  group_by(Outcome) %>%
  summarise(mean = mean(mean))

exp2 <- data2 %>%
  group_by(Outcome,Participant) %>%
  summarise(mean = mean(LookingTime))%>%
  group_by(Outcome) %>%
  summarise(mean = mean(mean))

exp3 <- data3 %>%
  group_by(Outcome,Participant) %>%
  summarise(mean = mean(LookingTime))%>%
  group_by(Outcome) %>%
  summarise(mean = mean(mean))

exp4 <- data4 %>%
  group_by(Outcome,Participant) %>%
  summarise(mean = mean(LookingTime))%>%
  group_by(Outcome) %>%
  summarise(mean = mean(mean))

exp5 <- data5 %>%
  group_by(Outcome,Participant) %>%
  summarise(mean = mean(LookingTime))%>%
  group_by(Outcome) %>%
  summarise(mean = mean(mean))

exp6 <- data6 %>%
  group_by(Outcome,Participant) %>%
  summarise(mean = mean(LookingTime))%>%
  group_by(Outcome) %>%
  summarise(mean = mean(mean))

```
# Target outcomes: Means and ANOVAs for Experiments 1-4
## Experiment 1 and 2
### Looking time
Both 12- and 19-month-olds looked longer at the inconsistent outcome, suggesting that they may have derived the identity of the object in
the cup through logical inference and were surprised when this conclusion was violated, as revealed by mean looking times, M [experiment 1, 19-month-olds (n = 24), Mconsistent = 7.7 s, Minconsistent = 10.5 s, F(1,23) = 5.79, P = 0.025; experiment 2, 12-month-olds 
(n=24),Mconsistent=6.2 s, Minconsistent= 7.6s, F(1,23) = 5.19, P = 0.032; repeated measures analyses of variance (ANOVAs)].

## Experiment 3 and 4
### Looking time
Both 19 and 12-month-olds looked longer at the inconsistent outcome (Fig. 2C), suggesting that they reacted to the logical gist of
a scene [experiment 3, 19-month-olds (n = 24), Mconsistent = 4.9 s, Minconsistent = 6.2 s, F(1,23) = 8.5, P = 0.008; experiment 4, 12-month-olds (n = 24),Mconsistent= 4.2 s,Minconsistent = 6.1 s, F(1,23) = 11, P = 0.003; repeated measures ANOVAs].

## Experiments 5 and 6
### Looking time (paradigm validation)
As expected at these ages, infants looked longer at an outcome inconsistent with the identity of the (known) object in the cup [experiment 5, 19-month-olds (n = 24), Mconsistent = 3.8 s, Minconsistent = 8.3 s, F(1,23) = 26.1, P = 0.0001; experiment 6, 12-month-olds (n =24), Mconsistent=4.9s, Minconsistent=6.2 s, F(1,23) = 4.9, P = 0.037; repeated measures ANOVAs].

### Check means reported for experiments 1-4
```{r}

## Means for Experiment 3
compareValues(reportedValue = 10.5, obtainedValue = exp1$mean[1], isP = F)
compareValues(reportedValue = 7.7, obtainedValue = exp1$mean[2], isP = F)

## Means for Experiment 2
compareValues(reportedValue = 7.6, obtainedValue = exp2$mean[1], isP = F)
compareValues(reportedValue = 6.2, obtainedValue = exp2$mean[2], isP = F)

## Means for Experiment 3
compareValues(reportedValue = 6.2, obtainedValue = exp3$mean[1], isP = F)
compareValues(reportedValue = 4.9, obtainedValue = exp3$mean[2], isP = F)

## Means for Experiment 4
compareValues(reportedValue = 6.1, obtainedValue = exp4$mean[1], isP = F)
compareValues(reportedValue = 4.2, obtainedValue = exp4$mean[2], isP = F)

## Means for Experiment 5
compareValues(reportedValue = 8.3, obtainedValue = exp5$mean[1], isP = F)
compareValues(reportedValue = 3.8, obtainedValue = exp5$mean[2], isP = F)

## Means for Experiment 6
compareValues(reportedValue = 6.2, obtainedValue = exp6$mean[1], isP = F)
compareValues(reportedValue = 4.9, obtainedValue = exp6$mean[2], isP = F)
```
### Check experiment 1 ANOVA values
```{r}
## wrangle data
d1 <- data1 %>%
  group_by(Outcome,Participant) %>%
  summarise(LookingTime = mean(LookingTime))

## compute anova
e1_anova = aov_ez("Participant","LookingTime",d1,within="Outcome")

## check values
compareValues(reportedValue = 5.79, obtainedValue = e1_anova$anova_table$F, isP = F)
compareValues(reportedValue = .025, obtainedValue = e1_anova$anova_table$`Pr(>F)`, isP = T)

```

### Check experiment 2 ANOVA values
```{r}
## wrangle data
d2 <- data2 %>%
  group_by(Outcome,Participant) %>%
  summarise(LookingTime = mean(LookingTime))

## compute anova
e2_anova = aov_ez("Participant","LookingTime",d2,within="Outcome")

## check values
compareValues(reportedValue = 5.19, obtainedValue = e2_anova$anova_table$F, isP = F)
compareValues(reportedValue = .032, obtainedValue = e2_anova$anova_table$`Pr(>F)`, isP = T)


```

### Check experiment 3 ANOVA values
```{r}
## wrangle data
d3 <- data3 %>%
  group_by(Outcome,Participant) %>%
  summarise(LookingTime = mean(LookingTime))

## compute anova
e3_anova = aov_ez("Participant","LookingTime",d3,within="Outcome")

## check values
compareValues(reportedValue = 8.5, obtainedValue = e3_anova$anova_table$F, isP = F)
compareValues(reportedValue = .008, obtainedValue = e3_anova$anova_table$`Pr(>F)`, isP = T)

```

### Check experiment 4 ANOVA values
```{r}
## wrangle data
d4 <- data4 %>%
  group_by(Outcome,Participant) %>%
  summarise(LookingTime = mean(LookingTime))

## compute anova
e4_anova = aov_ez("Participant","LookingTime",d4,within="Outcome")

## compare values
compareValues(reportedValue = 11, obtainedValue = e4_anova$anova_table$F, isP = F)
compareValues(reportedValue = .003, obtainedValue = e4_anova$anova_table$`Pr(>F)`, isP = T)

```

### Check experiment 5 ANOVA values
```{r}
## wrangle data
d5 <- data5 %>%
  group_by(Outcome,Participant) %>%
  summarise(LookingTime = mean(LookingTime))

## compute anova
e5_anova = aov_ez("Participant","LookingTime",d5,within="Outcome")

## compare values
compareValues(reportedValue = 26.1, obtainedValue = e5_anova$anova_table$F, isP = F)
compareValues(reportedValue = .0001, obtainedValue = e5_anova$anova_table$`Pr(>F)`, isP = T)

```

As expected at these ages, infants looked longer at an outcome inconsistent with the identity of the (known) object in the cup [experiment 5, 19-month-olds (n = 24), Mconsistent = 3.8 s, Minconsistent = 8.3 s, F(1,23) = 26.1, P = 0.0001; experiment 6, 12-month-olds (n =24), Mconsistent=4.9s, Minconsistent=6.2 s, F(1,23) = 4.9, P = 0.037; repeated measures ANOVAs].



### Check experiment 6 ANOVA values
```{r}
## wrangle data
d6 <- data6 %>%
  group_by(Outcome,Participant) %>%
  summarise(LookingTime = mean(LookingTime))

## compute anova
e6_anova = aov_ez("Participant","LookingTime",d6,within="Outcome")

## compare values
compareValues(reportedValue = 4.9, obtainedValue = e6_anova$anova_table$F, isP = F)
compareValues(reportedValue = .037, obtainedValue = e6_anova$anova_table$`Pr(>F)`, isP = T)

```



