---
title: "Cesana-Arlotti Permutation Analysis"
output: html_notebook
editor_options:
  chunk_output_type: inline
---

```{r}
knitr::opts_chunk$set(warning=F, cache=T, message=F)
```

```{r}
library(magrittr); library(tidyverse); library(eyetrackingR)
theme_set(ggthemes::theme_few())
```

Here we use the eyetrackingR package to reproduce the cluster analysis in Cesana-Arlotti et al (2018).

The analysis involves the following steps and the functions:

* use make_eyetrackingr_data() to get your raw dataframe from the output of the eye-tracker

* use make_time_sequence_data() to creates time-bins and summarizes proportion-looking within each time-bin

* use make_time_cluster_data() to find adjacent time bins that pass some test-statistic threshold, and assigns these adjacent bins into groups (clusters). Supports t.test, wilcox.test, (g)lm, and (g)lmer. Which one should we use?

* Use analyze_time_clusters() to take a summed statistic for each cluster, and compares it to the "null" distribution of sum statistics obtained by shuffling/resampling the data and extracting the largest cluster from each resample.

```{r example}
data(word_recognition)

data <- make_eyetrackingr_data(word_recognition, 
                       participant_column = "ParticipantName",
                       trial_column = "Trial",
                       time_column = "TimeFromTrialOnset",
                       trackloss_column = "TrackLoss",
                       aoi_columns = c('Animate','Inanimate'),
                       treat_non_aoi_looks_as_missing = TRUE
                )

# subset to response window post word-onset
response_window <- subset_by_window(data, 
                                    window_start_time = 15500, 
                                    window_end_time = 21000, 
                                    rezero = FALSE)
```

```{r}
# analyze amount of trackloss by subjects and trials
(trackloss <- trackloss_analysis(data = response_window))

# remove trials with > 25% of trackloss
response_window_clean <- clean_by_trackloss(data = response_window,
                                            trial_prop_thresh = .25)
```


```{r}
# create Target condition column
response_window_clean$Target <- as.factor( ifelse(test = grepl('(Spoon|Bottle)', response_window_clean$Trial), 
                                       yes = 'Inanimate', 
                                       no  = 'Animate') )
```


```{r}
response_time <- make_time_sequence_data(response_window_clean,
                                  time_bin_size = 100, 
                                  predictor_columns = c("Target"),
                                  aois = "Animate",
                                  summarize_by = "ParticipantName" )

# visualize timecourse
plot(response_time, predictor_column = "Target") + 
  theme_light() +
  coord_cartesian(ylim = c(0,1))
```


```{r}
num_sub = length(unique((response_window_clean$ParticipantName)))
threshold_t = qt(p = 1 - .05/2, 
                 df = num_sub-1) # pick threshold t based on alpha = .05 two tailed
```


```{r}
df_timeclust <- make_time_cluster_data(response_time, 
                                      test= "t.test", paired=TRUE,
                                      predictor_column = "Target", 
                                      threshold = threshold_t) 
plot(df_timeclust) +  ylab("T-Statistic") + theme_light()
```


```{r}
summary(df_timeclust)
```

```{r}
clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=TRUE, paired=TRUE,
                                        samples=150) # in practice, you should use a lot more
```

```{r}
plot(clust_analysis) + theme_light()
```

```{r}
summary(clust_analysis)
```

