---
title: "Cesana et al: Means and ANOVA results, Exp 1-4"
author: ""
date: "17 4 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(CODreports) # custom report functions
library(afex)
library(langcog)
```

```{r data processing}
data1 <- read_tsv("../data/InfantsData/ByParticipant_LookingTimeAndOculomotorMeasures/E3-byParticipant.txt") %>%
  mutate(age = "19mo",
         condition = "inference",
         Participant = paste(Participant,age,condition,sep="_"))

data2 <- read_tsv("../data/InfantsData/ByParticipant_LookingTimeAndOculomotorMeasures/E4-byParticipant.txt") %>%
  # Column names in this data file are different from the others
  set_colnames(c("Participant","LTDiff","Shift","X","PD"))%>%
  mutate(age = "12mo",
         condition = "inference",
         Participant = paste(Participant,age,condition,sep="_"))

data3 <- read_tsv("../data/InfantsData/ByParticipant_LookingTimeAndOculomotorMeasures/E5-byParticipant.txt") %>%
  mutate(age = "19mo",
         condition = "no_inference",
         Participant = paste(Participant,age,condition,sep="_"))

data4 <- read_tsv("../data/InfantsData/ByParticipant_LookingTimeAndOculomotorMeasures/E6-byParticipant.txt") %>%
  mutate(age = "12mo",
         condition = "no_inference",
         Participant = paste(Participant,age,condition,sep="_"))

data <- bind_rows(data1,data2,data3,data4)

str(data)
```

# Target outcomes: Means and ANOVAs for Switch Analysis
## Data from Experiments 3-5
By the end of this phase, infants also displaced their eyes toward the cup more markedly (Fig. 3, B and C, and supplemen- tary materials) and switched their focus from the visible object to the cup in more trials (Minference = 71%, Mno_inference = 50%, F1,88 = 10.4, P = 0.002, two-way ANOVA; fig. S2 and supplementary
materials) when a deduction was needed than when it was not.

### Check means reported
```{r}
## Means for switching by condition (as reported in the paper)
data %>%
  group_by(condition)%>%
  summarise(mean = mean(Shift))

## Means for switching by condition and age (not reported in the paper)
data %>%
  group_by(condition,age)%>%
  summarise(mean = mean(Shift))


## Means for switching in inference condition
compareValues(reportedValue = 0.71, obtainedValue = mean(data$Shift[data$condition=="inference"]) , isP = F)


## Means for switching in no inference condition
compareValues(reportedValue = 0.50, obtainedValue = mean(data$Shift[data$condition=="no_inference"]) , isP = F)


```
### Check ANOVA values
```{r}
## compute anova
e1_anova = aov_ez("Participant","Shift",data,between=c("age","condition"))

## check values
compareValues(reportedValue = 10.4, obtainedValue = e1_anova$anova_table$F[2], isP = F)
compareValues(reportedValue = .002, obtainedValue = e1_anova$anova_table$`Pr(>F)`[2], isP = T)

```
### Plot and comparison by age group
```{r}
## t tests for each age group separately

t.test(Shift ~ condition, data = data%>%filter(age=="12mo"))

t.test(Shift ~ condition, data = data%>%filter(age=="19mo"))


d.p <- data %>%
  group_by(condition, age)%>%
  multi_boot_standard(col = "Shift")

ggplot() +
  geom_jitter(data = data, aes(x = age , y = Shift, alpha = .2, col = condition), width = .1,height = .0)+
  geom_pointrange(data = d.p,aes(x = age, y = mean, col = condition ,ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 1) + 
  guides(alpha = F)+
  ggtitle("Shift analysis")+
  theme_few() + 
  scale_colour_solarized()



```
